Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-22 doc/JFLA2022/Slides/Slides.tex
last changes in Slides ?

         \input{../../movies/snippets/Canon/canonExamplesb}
       \item Not the same definition as in K. \& S.'s article, but same abstract properties (monotony, limits, \dots).
       \end{itemize}
     \end{block}
\end{frame}

@@

    \frametitle{Paths and accessibility}
    \begin{block}{ }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

@@

\only<2>{{\color{lookcolor}OK for large enough $i$ (K. \& S., 1981)}}
\vspace{6pt}

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles
  (stronger than \textcolor{banyuls}{Banyuls 2018}).
}

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}
  \begin{block}{}
    \begin{itemize}

    \item  Links with other representations of ordinals, \emph{e.g.}:
  \begin{footnotesize}
    {\color{blue}
\begin{verbatim}
(* Minki Cho *)
Inductive Ord.t :=
| Ord.build: forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
      }
 \end{footnotesize}

      \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item More examples and exercises
     \end{itemize}
  \end{block}

  \begin{block}{}
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please clone, fork, contribute!}
      \begin{itemize}
      \item New chapters
      \item Any correction or suggestion of improvement (text and/or proofs).

@@

>>>>

         \input{../../movies/snippets/Canon/canonExamplesb}
       \item Not the same definition as in K. \& S.'s article, but same abstract properties (monotony, limits, \dots). Sounds to be extentionally the same function.
       \end{itemize}
     \end{block}
\end{frame}

@@

    \frametitle{Example: Paths and accessibility}
    \begin{block}{ }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

@@

\only<2>{{\color{lookcolor}OK for large enough $i$ ! (K. \& S., 1981)}}
\vspace{6pt}

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of \textcolor{lookcolor}{\emph{the considered kind of}} hydra battles
  (stronger than \textcolor{banyuls}{Banyuls 2018}).
}

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}

    \begin{itemize}

 \item Relation text/formalization,  new toolchain for \alectr
 \item More illustrations of proof and specification patterns,  new exercises
       \item New chapters (algorithmics, geometry ?)
 \end{itemize}

 \vspace{8pt}

   \begin{itemize}
 \item Develop the \texttt{Hydra-Gaia} part (more integration).
 \item More results about hyper-complexity and fast growing functions
 \item  Links with other representations of ordinals, \emph{e.g.}:
  \begin{footnotesize}
    {\color{blue}
\begin{verbatim}
(** By Minki Cho **)
Inductive Ord.t :=
| Ord.build: forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
      }
    \end{footnotesize}

@@

  \begin{block}{}
  {\it \Hydras and  \community are on GitHub. Please clone, fork, comment, raise issues, contribute!}
\end{block}
